---
title: "QoL Data_Analysis_notebook"
author: "Yunbo Zhu"
date: "1/7/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose of this Analysis
Give a first glimpse on Columbia University's 2019 Quality of Life Survey data and provide foundamental suggestions

## Step 1
Import the data set from the driven location and clean the data
```{r}
library(tidyverse)
library(readxl)
mydata<-read_excel("/Users/katherine/Desktop/test_data.xlsx")
```

## Step 2: Visualization
i. Create a histogram of respondents according to their program (M.S, PhD, etc.)
```{r echo=FALSE}
colnames(mydata)<-c('department','program','Themed social events','Off-Campus socials',
                    'Interschool events','Performance Arts','Events organized by student groups',
                    'Entertainment','PDL core Module')
mydata<-mydata[-1,]%>%drop_na(department,program)
histplot<-ggplot(mydata,aes(program))+
  geom_histogram(stat = "count")+
  labs(title = "histogram of respondents")+theme_classic()+coord_flip()
  theme(plot.title = element_text(hjust = 0.5))
histplot
```

ii. Create a pie-chart representing the percentage of respondents by department
```{r}
data<-mydata%>%group_by(department)%>%summarise(count = n())%>%arrange(desc(department))%>%
  mutate(prop = count/sum(count)*100)%>%
  mutate(ypos = cumsum(prop)-0.5*prop)%>%
  mutate(abbr = abbreviate(department))
piechart<-ggplot(data,aes(x = "",y = prop,fill = department))+
  geom_bar(stat = "identity",width = 1,color = "white")+
  coord_polar("y",start = 0)+theme_void()+
  geom_text(aes(y = ypos,label = abbr),color = "black",size = 2)+
  scale_fill_brewer(palette = "Spectral")
piechart
```

## Step 3: Data Exploration
**i. How do the respondents feel about PDL core classes?**

From the table below, there are more then half of the respondents satisfy with the PDL core classes and there are 
about 17% the of the respondents strongly satisfy with the classes. So in all, most of the respondents (about 70%)
are satified with the PDL core classes
```{r}
data_pdl<-mydata%>%drop_na()%>%group_by(`PDL core Module`)%>%
  summarise(count = n())%>%mutate(perc = count/sum(count))
data_pdl
```

**ii. To Determine which department is the most satisfied with PDL core classes?**

From the table below, Electrical Engineering department has the most percentage of satisfied rate (Agree and Strongly Agree with the PDL)
```{r}
data_pdl2<-mydata%>%drop_na()%>%
  group_by(department,`PDL core Module`)%>%
  summarise(count = n())%>%
  mutate(perc = count/sum(count))%>%
  filter(`PDL core Module`%in%c('Agree','Strongly agree'))%>%
  summarise(satisfied = sum(perc))%>%
  arrange(desc(satisfied))
data_pdl2
```

## Step 4: Summary
From the visualization of all five events, interschool events (Festifall, Mel's Burger Bar Mixer, Poker Night, etc.)
and off-campus socials (Boat Cruise, Rooftop socials, etc.) are more welcomed by respondents. 
I would recommend the student council to put more budget on these two types of events or hold more of them. Also, 
apparently from the plot, the percentage of neutral position (Neither agree nor disagree) is higher compared with survey
on PDL classes. So I recommend the Student Council to collect suggestions from the respondents that what other kind of 
events they want.

```{r}
data_events<-mydata%>%drop_na()%>%
  pivot_longer(3:7,names_to = "events",values_to = "satisfy or not")%>%
  group_by(events,`satisfy or not`)%>%count()
event_plot<-ggplot(data_events,aes(x = "",y = n,fill =`satisfy or not`))+
  geom_bar(stat = "identity",width = 1,color = "white")+
  coord_polar("y",start = 0)+
  theme_void()+
  facet_wrap(~events)
event_plot
```
